\papertitle

### 2014-03-18 final-report/paper.tex
results section

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{\papertitle}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{ Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

\begin{itemize}
    \item problem: hard to learn why a query is slow
    \item motivation: help developers/programmers dig what the problems might be
\end{itemize}

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

@@

@@

\textbf{Graph Rendering:} We use D3 to render the \graph graph, which allows us to support various interactions and transitions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.

@@

In this section we will evaluate the different visualizations and elaborate on actual examples where the visualization helped us to find data or execution skew.

@@

\subsection{Network visualization}

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

\title{\papertitle}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

\begin{itemize}
    \item problem: hard to learn why a query is slow
    \item motivation: help developers/programmers dig what the problems might be
    \item Questions: find data/execution skew, identify performance bottlenecks, visualize data flow in the system (elaborate on each point)...
\end{itemize}

@@

The Myria web front-end server is written in Python and runs on Google App Engine\footnote{\url{https://developers.google.com/appengine/}}. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualization on the web. We used visualization techniques such as \emph{focus+context}\cite{furnas1986generalized} that possible to implement conveniently using D3.

@@

% Figures
% 1: Graph with back-edge
% 2: Large Graph expanded vs. large Graph reduced vs. large graph expanded -1

@@

\textbf{Graph Rendering:} We use D3 \cite{d3} to render the \graph graph, which allows us to support various interactions and transistions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.

@@

We used \system to examine real world database queries that ran on Myria. We base our analysis on the different visualizations that were generated by \system and present examples where the \system helped us better identify (1) data skew, (2) execution skew, (3) performance bottlenecks.

We explore a simple join query we performed on one million tuples extracted from Twitter data. This query joins Twitter followers and followees by user ID. The query written in SQL is expressed below.

\begin{lstlisting}
SELECT *
FROM twitter S, twitter R
WHERE S.follower = R.followee
\end{lstlisting}

The resulting \graph visualization is displayed in ~\ref{fig:TODO}. The user will navigate the \graph visualization in the browser panel in the next case studies to identify several performance symptoms.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall View}

%dom

\subsection{Case 1: Identifying Data Skew using the \network View}
